Age-related changes in plant growth and traits

### 2015-08-19 Growth_figs.rmd
Attempt at simplifying color and label selection

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.mature[as.factor(data[[spp]]$mature)])
}

mtext("Vegetative investment", 2, outer=TRUE,cex=1.2)
mtext("proportion maximum H", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
  abline(0,1)
}

mtext("increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=0.9,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
  abline(0,1)
}

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
plot(LL_death~shoot_leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp[as.factor(species)])
mod <- lm(log(shoot_leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
words.top.right.logx(mod)

plot(LL_death~leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp[as.factor(species)])
mod <- lm(log(leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
words.top.right.logx(mod)
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("ll death", 2, outer=TRUE,cex=1.2)
mtext("shoot leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("ll death", 2, outer=TRUE,cex=1.2)
mtext("leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")

@@

***growth stem diam vs. prop maxH***
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
plot(growth_stem_diameter~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("growth_stem_diameter", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
```

***growth leaf area vs. prop maxH***
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
plot(growth_leaf_area~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("increase in leaf area", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("total size", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.mature[as.factor(data[[spp]]$mature)])
}

mtext("total size", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
```

@@

plot(wood_density~growth_leaf_area,SummaryInd,log="y",pch=16,col=col.age[as.factor(age)])
mod <- lm(log(growth_leaf_area)~age*wood_density,SummaryInd)
summary(mod)
```

>>>>

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.mature(data[[spp]]$mature)
}

mtext("Vegetative investment", 2, outer=TRUE,cex=1.2)
mtext("proportion maximum H", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
  abline(0,1)
}

mtext("increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=0.9,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
  abline(0,1)
}

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
plot(LL_death~shoot_leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
mod <- lm(log(shoot_leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
words.top.right.logx(mod)

plot(LL_death~leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
mod <- lm(log(leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
words.top.right.logx(mod)
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("ll death", 2, outer=TRUE,cex=1.2)
mtext("shoot leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("ll death", 2, outer=TRUE,cex=1.2)
mtext("leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")

@@

***growth stem diam vs. prop maxH***
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
plot(growth_stem_diameter~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp(species))
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("growth_stem_diameter", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

***growth leaf area vs. prop maxH***
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
plot(growth_leaf_area~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp(species))
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("increase in leaf area", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("total size", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.mature(data[[spp]]$mature)
}

mtext("total size", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```

@@

plot(wood_density~growth_leaf_area,SummaryInd,log="y",pch=16,col=col.age(age)
mod <- lm(log(growth_leaf_area)~age*wood_density,SummaryInd)
summary(mod)
```

### 2015-08-19 Panalysis.rmd
Attempt at simplifying color and label selection

mod <- lm(log(repro_inv)~log((propagule_inv)),data=subset(SummaryInd,repro_inv>0&propagule_inv>0))
plot(propagule_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,repro_inv>0&prop_propagule>0))
plot(asin(sqrt(prop_propagule))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(repro_inv)~log((prepollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_aborted_inv>0))
plot(prepollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0))
plot(asin(sqrt(prop_prepollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(repro_inv)~log((prepollen_success_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_success_inv>0))
plot(prepollen_success_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0))
plot(asin(sqrt(prop_prepollen_success))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(repro_inv)~log((packaging_dispersal_inv)),data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0))
plot(packaging_dispersal_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
abline(0,1)
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(repro_inv)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0))
plot(asin(sqrt(prop_packaging_dispersal))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(repro_inv)~log((postpollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0))
plot(postpollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0))
plot(asin(sqrt(prop_postpollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
words.bottom.left.logx(mod)
```

@@

par(mfrow=c(1,1), cex=1, omi=c(.8,.8,.1,.1), mai=c(1.1,1,.4,0.2)) 
plot(asin(sqrt(prop_growth_stem_diam))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0),pch=16,col=col.spp[as.factor(species)])
mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_growth_stem_diam)),data=subset(SummaryInd,RA>0))
words.bottom.left(mod)
```

>>>>

mod <- lm(log(repro_inv)~log((propagule_inv)),data=subset(SummaryInd,repro_inv>0&propagule_inv>0))
plot(propagule_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&propagule_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to propagules (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,repro_inv>0&prop_propagule>0))
plot(asin(sqrt(prop_propagule))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_propagule>0), log="x", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(repro_inv)~log((prepollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_aborted_inv>0))
plot(prepollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination aborted tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0))
plot(asin(sqrt(prop_prepollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(repro_inv)~log((prepollen_success_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_success_inv>0))
plot(prepollen_success_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination successful tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0))
plot(asin(sqrt(prop_prepollen_success))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(repro_inv)~log((packaging_dispersal_inv)),data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0))
plot(packaging_dispersal_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to packaging and dispersal (mg)")
abline(0,1)
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(repro_inv)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0))
plot(asin(sqrt(prop_packaging_dispersal))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(repro_inv)~log((postpollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0))
plot(postpollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to tissues aborted postpollination (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0))
plot(asin(sqrt(prop_postpollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
words.bottom.left.logx(mod)
```

@@

par(mfrow=c(1,1), cex=1, omi=c(.8,.8,.1,.1), mai=c(1.1,1,.4,0.2)) 
plot(asin(sqrt(prop_growth_stem_diameter))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0),pch=16,col=col.spp(species))
mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_growth_stem_diameter)),data=subset(SummaryInd,RA>0))
words.bottom.left(mod)
```
